Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering

### 2014-09-11 evaluation.tex
imported an authcomments package from Andrew Myers

ED: We need to point out that these monitors cannot be implemented with a simple
1-bit dataflow engine (DIFT) that we use for filtering. 
Point: address potential reviewer questions on why don't we just use a 
programmable dataflow engine for monitoring.

@@

ED: we need to better justify the high overhead. 
Key points: 1) the overhead is in line with LBA, which represent multi-core
monitoring w/ low HW costs.
2) If we are going to mention dynamic memory allocation. We need to say why
it's really necessary -- it's not our implementation problem. It's something
that you need to have for large meta-data. Also, I don't think UMC would need
dynamic allocation.

>>>>

\ED{We need to point out that these monitors cannot be implemented with a simple
1-bit dataflow engine (DIFT) that we use for filtering. 
Point: address potential reviewer questions on why don't we just use a 
programmable dataflow engine for monitoring.}

@@

\ED{we need to better justify the high overhead. 
Key points: 1) the overhead is in line with LBA, which represent multi-core
monitoring w/ low HW costs.
2) If we are going to mention dynamic memory allocation. We need to say why
it's really necessary -- it's not our implementation problem. It's something
that you need to have for large meta-data. Also, I don't think UMC would need
dynamic allocation.}
